Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-06-14 Journal1/Response3/Response.tex

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied. The main contributions of this paper are summarized as follows:
\begin{itemize}
\item The paper presents a network slicing model for three 5G services: eMBB, mMTC, and URLLC. We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on different types of services with different QoS and service priorities, we formulate a problem for allocating baseband resources to maximize the weighted throughput of O-RAN.
\item The focus of our paper is on the multi-service resource management of the RAN, slicing in the flexibility, openness, and openness of the O-RAN architecture.
\item We propose an algorithm for resource management in a two-step, with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
In the first step, we reformulate and simplify the problem to find an upper and lower bound for the number of activated VNFs and use the Lagrangian function and KKT conditions to find optimal power and PRB allocation. For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\item We perform numerical experiments to analyze the performance of the proposed algorithm, which proves to have a higher data rate than both the baseline scheme and data-driven method. Interestingly, our results show that this algorithm performs close to the optimal solution in low interference.
\end{itemize}

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment5:} `` In a similar fashion, the authors have not considered the Reviewer’s suggestion to move the Related Work as a separate Section in order to improve the flow and clarity of the Introduction. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I changed the background from sub-section to the section part.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} `` Regarding the Reviewer’s comment with respect to the network slice management, whereas the authors have introduced the 4 stages of the life cycle of a network slice, the connection to their approach is very vague. It is still not clear how this process is achieved and how it is linked to their method. I was expecting at least a connection or introduction to Fig.1 where the system is shown. Additionally, more information with respect to the interaction with the system would have been required in that regard. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We add the following part to the slice management section.

In the preparation phase, firstly, the evaluation of requirements is considered. Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times. Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation. In this phase, we can use our algorithm after estimating the system's traffic.
 As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC. For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF. Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices. Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles. 
After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started. In this phase, the slices are created based on the previous phase. If the evaluation changes, the slice's resources can be modified.
We can use our algorithm to assign resources to the services in the operation phase.
If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment6:} ``With respect to the convergence time of the algorithm, the Reviewer had made a suggestion to the authors to include it in the current version of the manuscript, yet the authors do not seem to have done that. The authors’ response points to Fig. 11. However if one looks at Fig.11 carefully, understands that only the Aggregate throughput is shown there. Even if one considers the Section III-C1 and III-C2 that the authors demonstrate as their convergence analysis and proof, there is no evidence or clarification of any delay value with respect to their algorithm’s convergence. On the one hand it is very beneficial to have a mathematical proof that the algorithm converges. On the other hand, it is equally important to portray these findings with numerical values. In any case, this is not applicable in the current version of the manuscript. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}

### 2022-06-14 Journal1/paper5TNSM/pr.tex
last version of revised paper

\subsection{Slice Management}
In this subsection, we will look at the life cycle of network slicing on a practical level. 
The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
\end{itemize}
In the preparation phase, the evaluation of requirements is considered. After that, we use our algorithm to find the optimal number of VNFs for each slice and PRB assignment and power allocation. Therefore, in the preparation phase, we estimate our resource of slices, and in the commission phase, we allocate our resources to the slices.
%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

>>>>

\subsection{Slice Management}
In this subsection, we will look at the life cycle of network slicing on a practical level. 
The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
\end{itemize}
\textcolor{MidnightBlue}{In the preparation phase, firstly, the evaluation of requirements is considered. Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times. Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation. In this phase, we can use our algorithm after estimating the system's traffic.
As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC. For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF. Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices. Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.  
After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started. In this phase, the slices are created based on the previous phase. If the evaluation changes, the slice's resources can be modified.
We can use our algorithm to assign resources to the services in the operation phase.
If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.}
%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.
